\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{array}
\usepackage{fancyhdr}

\geometry{margin=1.5cm, top=2cm, bottom=2cm}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{LLM Hand Annotation Experiment}
\fancyhead[R]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

\definecolor{posgreen}{RGB}{220,255,220}
\definecolor{negred}{RGB}{255,220,220}
\definecolor{ruleblue}{RGB}{230,240,255}

\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}

\title{\textbf{LLM Hand Annotation Dataset}\\[0.5em]\large Blind Descriptions of Card Hands for 20 Rules}
\author{Generated with Ollama qwen2.5-coder:7b}
\date{December 2024}

\begin{document}
\maketitle

\section*{Overview}
This document contains blind LLM annotations of card hands. For each rule:
\begin{itemize}
    \item \textbf{5 positive hands} (satisfy the rule) -- highlighted in \colorbox{posgreen}{green}
    \item \textbf{5 negative hands} (violate the rule) -- highlighted in \colorbox{negred}{red}
\end{itemize}

The LLM described each hand \textbf{without knowing the rule}, focusing only on observable features.

\vspace{1em}
\noindent\textbf{Statistics:}
\begin{itemize}
    \item 20 rules across 11 families
    \item 200 total hands annotated
    \item Average description length: 9.0 tokens
    \item Unique vocabulary: 355 tokens
\end{itemize}

\newpage


\subsection*{\colorbox{ruleblue}{\strut Sorted\_by\_rank} (LOCAL)}
\textbf{Rule:} Ranks are in non-decreasing order

\begin{longtable}{C{0.5cm} L{4.5cm} L{9cm}}
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endfirsthead
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endhead
\rowcolor{posgreen} + & 2ظآب 4ظآخ 5ظآح 7ظآح 10ظآب Aظآب & One black ace, two spades, one heart. \\
\rowcolor{posgreen} + & 7ظآح Jظآخ Jظآب Qظآح Qظآث Aظآخ & Ace high, two jacks, queen flush, red hearts. \\
\rowcolor{posgreen} + & 3ظآح 3ظآب 8ظآب 9ظآث Jظآح Jظآح & Black jacks and a pair of threes. \\
\rowcolor{posgreen} + & 2ظآخ 5ظآخ 5ظآث 9ظآخ Kظآث Kظآث & Two reds, two blacks, one pair. \\
\rowcolor{posgreen} + & 6ظآخ 6ظآب 10ظآخ 10ظآب Kظآث Kظآخ & Two-pair, one heart. \\
\rowcolor{negred} -- & Jظآح 8ظآح 3ظآح 4ظآب Aظآخ Qظآث & Red hearts, black spades, and a rare combo. \\
\rowcolor{negred} -- & 6ظآب 2ظآخ Qظآح Kظآح 6ظآث Jظآح & High spades, diamonds, and hearts; jacks, queens, kings; red cards. \\
\rowcolor{negred} -- & Kظآب Qظآح Kظآث 3ظآخ Aظآخ Kظآث & Three Kings and an Ace, alternating red and black. \\
\rowcolor{negred} -- & 5ظآب 4ظآخ 3ظآح 9ظآث 7ظآح 6ظآخ & 5ظآب 4ظآخ 3ظآح 9ظآث 7ظآح 6ظآخ - Mixed suits, two reds, two blacks, sequential ranks. \\
\rowcolor{negred} -- & Aظآب 2ظآح Aظآح 10ظآخ 3ظآث Aظآح & Ace of hearts, two hearts, third club, ten diamonds. \\
\bottomrule
\end{longtable}


\subsection*{\colorbox{ruleblue}{\strut Ends\_same\_suit} (LOCAL)}
\textbf{Rule:} First and last share the suit

\begin{longtable}{C{0.5cm} L{4.5cm} L{9cm}}
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endfirsthead
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endhead
\rowcolor{posgreen} + & Aظآث 8ظآخ Jظآخ 2ظآب 9ظآح 5ظآث & Black spade, red hearts, mixed colors; diamond trio, black clubs. \\
\rowcolor{posgreen} + & 7ظآخ 6ظآب Aظآب 10ظآخ Qظآث 10ظآخ & Four of a kind: ظآخ10. High card: Aظآب. \\
\rowcolor{posgreen} + & 3ظآث 10ظآخ 6ظآب 4ظآخ Jظآخ 9ظآث & Red and black, mixed suits, high and low cards. \\
\rowcolor{posgreen} + & 4ظآح 2ظآث 5ظآث Jظآث Aظآخ 5ظآح & Four hearts, a spade, and an ace; mixed colors, sequential ranks. \\
\rowcolor{posgreen} + & Jظآب 8ظآب Aظآب Kظآث 3ظآخ 2ظآب & Black Jacks and Kings; red Ace, Three, Two. \\
\rowcolor{negred} -- & 4ظآب 8ظآخ 7ظآخ 5ظآب Jظآث 6ظآث & Spades and clubs, alternating colors, mixed ranks. \\
\rowcolor{negred} -- & Qظآث 4ظآب 4ظآخ Kظآح 6ظآث Qظآب & Two queens, a king, and a pair of fours; clubs and spades mixed. \\
\rowcolor{negred} -- & 5ظآب 8ظآخ 9ظآخ 6ظآخ Aظآث 8ظآث & Two sets of two clubs and a spade, alternating red and black. \\
\rowcolor{negred} -- & 2ظآخ 6ظآب 8ظآث Kظآب 2ظآخ 10ظآب & Two deuces, king, and ten mixed in a red-black pattern. \\
\rowcolor{negred} -- & Kظآخ 6ظآب 3ظآث Qظآث 4ظآح 7ظآح & Two reds, two blacks, high spade, queen club. \\
\bottomrule
\end{longtable}


\subsection*{\colorbox{ruleblue}{\strut Ends\_same\_color} (LOCAL)}
\textbf{Rule:} First and last share the color

\begin{longtable}{C{0.5cm} L{4.5cm} L{9cm}}
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endfirsthead
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endhead
\rowcolor{posgreen} + & 2ظآح 7ظآث Kظآب 2ظآخ Aظآب 4ظآخ & Two hearts, a spade, and a diamond; one red, two black. \\
\rowcolor{posgreen} + & 4ظآث 10ظآث 8ظآث 2ظآب 4ظآب 10ظآب & Four of a kind, black clubs and spades. \\
\rowcolor{posgreen} + & Kظآب Qظآب 8ظآح 7ظآح Aظآث 6ظآث & Black, alternating colors, high-ranking spades lead with ace. \\
\rowcolor{posgreen} + & 3ظآث 9ظآث 9ظآح 8ظآث Aظآخ 8ظآب & Black 3, 2 red 9s, black 8, spade Ace. \\
\rowcolor{posgreen} + & 5ظآث 6ظآث 3ظآث Jظآب Kظآح 10ظآب & Black suited clubs 3-6. Jack and King of red hearts, 10 of black spades. \\
\rowcolor{negred} -- & Jظآب 4ظآب Kظآخ 5ظآخ 8ظآخ 10ظآح & Black Jacks and Kings with a red 10. \\
\rowcolor{negred} -- & Jظآخ 5ظآخ 8ظآث Kظآب 8ظآح 6ظآب & Jظآخ 5ظآخ 8ظآث Kظآب 8ظآح 6ظآب - Two pairs: Jack and 8; King singleton. Clubs and spades. Different colors. \\
\rowcolor{negred} -- & Aظآح 10ظآب Jظآخ Kظآث 8ظآح 10ظآث & A pair of tens with a king and jack. \\
\rowcolor{negred} -- & Kظآخ 4ظآب 2ظآح 5ظآح 2ظآخ 10ظآب & Two reds, two blacks; high king, low two; alternating clubs and spades. \\
\rowcolor{negred} -- & 6ظآث 8ظآح 8ظآح 5ظآح 7ظآث 3ظآخ & Double hearts, mixed colors. \\
\bottomrule
\end{longtable}


\subsection*{\colorbox{ruleblue}{\strut Has\_pair\_ranks} (COUNT)}
\textbf{Rule:} At least one pair (same rank)

\begin{longtable}{C{0.5cm} L{4.5cm} L{9cm}}
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endfirsthead
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endhead
\rowcolor{posgreen} + & Kظآخ 8ظآح 10ظآخ 10ظآب 2ظآث Aظآب & Spade Ace, Diamond King, Red Jack, Black 10s, Club 2. \\
\rowcolor{posgreen} + & Qظآح 4ظآب 4ظآب Qظآث 5ظآب 9ظآح & Four of a kind in spades and hearts. \\
\rowcolor{posgreen} + & 9ظآث 7ظآب Jظآخ Kظآح 6ظآث Jظآح & One red and two black jacks; high-ranking clubs and spades. \\
\rowcolor{posgreen} + & 4ظآح 7ظآخ 4ظآخ 7ظآخ Aظآخ Jظآث & Four of a kind (Hearts), Jack of Clubs. \\
\rowcolor{posgreen} + & 2ظآث Kظآخ Kظآث 4ظآث 3ظآخ 10ظآح & Three-of-a-kind (Kظآخ, Kظآث) with a pair (2ظآث, 3ظآخ), deuces and tens. \\
\rowcolor{negred} -- & 2ظآث 5ظآث 7ظآث 4ظآث 6ظآح Kظآث & Black suits dominate with a heart kicker. \\
\rowcolor{negred} -- & Qظآث 5ظآب 3ظآب 9ظآخ Kظآث Aظآح & Two red aces, three black cards, alternating diamond and spade. \\
\rowcolor{negred} -- & 4ظآخ 9ظآح 5ظآح Aظآث Kظآب 10ظآح & High heart flush with aces and kings. \\
\rowcolor{negred} -- & Qظآب 9ظآث 2ظآخ 10ظآب 4ظآخ 8ظآخ & Black and red hearts, alternating ranks. \\
\rowcolor{negred} -- & 3ظآخ 5ظآب 4ظآخ 8ظآث 7ظآث 10ظآب & Red hearts and black clubs; alternating odd-even ranks. \\
\bottomrule
\end{longtable}


\subsection*{\colorbox{ruleblue}{\strut Uniform\_color} (COUNT)}
\textbf{Rule:} All cards have the same color

\begin{longtable}{C{0.5cm} L{4.5cm} L{9cm}}
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endfirsthead
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endhead
\rowcolor{posgreen} + & 8ظآب Aظآب Kظآب 10ظآب Qظآث 2ظآب & Black spades reign supreme; ace, king, queen lead. \\
\rowcolor{posgreen} + & Kظآح 9ظآح Aظآخ Jظآح 5ظآح Kظآح & Royal flush with a king. \\
\rowcolor{posgreen} + & 2ظآح 9ظآخ 7ظآح 4ظآخ 8ظآخ Qظآح & Mixed hearts and diamonds; one high, two low, one queen. \\
\rowcolor{posgreen} + & Jظآث 2ظآث 7ظآث Qظآب 7ظآب Jظآث & Black jacks and queens with red sevens. \\
\rowcolor{posgreen} + & 5ظآخ 4ظآخ Kظآح Jظآح 5ظآخ Jظآخ & Two pairs, one red, one black. \\
\rowcolor{negred} -- & 3ظآث 3ظآخ 7ظآث Qظآخ 6ظآب 6ظآب & Two threes and two sixes, one queen in a mixed suit. \\
\rowcolor{negred} -- & Kظآخ Jظآث 6ظآخ 5ظآب 5ظآث 8ظآح & Two pairs, one high; hearts and spades mixed. \\
\rowcolor{negred} -- & Kظآث Jظآح 2ظآح 4ظآخ 6ظآب 7ظآب & Black jack, red jacks, heart twos, double spades. \\
\rowcolor{negred} -- & 8ظآخ Qظآح Qظآح Kظآخ 8ظآب Jظآب & QظآخKظآخ8ظآخ8ظآبJظآب. Three queens and a king in the same suit, with an 8 and Jack of spades. \\
\rowcolor{negred} -- & 7ظآخ 6ظآخ 7ظآح 2ظآث Aظآخ Qظآب & Seven of hearts, six of diamonds, ace of diamonds, queen of spades. \\
\bottomrule
\end{longtable}


\subsection*{\colorbox{ruleblue}{\strut Exactly\_two\_suits} (COUNT)}
\textbf{Rule:} Exactly two suits appear

\begin{longtable}{C{0.5cm} L{4.5cm} L{9cm}}
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endfirsthead
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endhead
\rowcolor{posgreen} + & 10ظآب Kظآب Kظآب 7ظآث Aظآث Jظآث & Black suited kings and aces. \\
\rowcolor{posgreen} + & 4ظآح 7ظآب Qظآح 6ظآب Kظآح Jظآب & Four hearts, three spades; queens and kings together. \\
\rowcolor{posgreen} + & 5ظآب 5ظآب 3ظآخ Aظآخ 3ظآخ Kظآب & Black Jacks, Red Tens, Two Spades. \\
\rowcolor{posgreen} + & Kظآب 3ظآح 2ظآب Qظآح 3ظآب 7ظآح & Black king, red threes, black two, red queen, black three, red seven. Two reds, two \\
\rowcolor{posgreen} + & 6ظآح Aظآح 3ظآخ 4ظآخ 3ظآخ 4ظآخ & Double red suits, sequential pairs. \\
\rowcolor{negred} -- & Qظآث Kظآخ 9ظآب 6ظآث 7ظآب 5ظآب & Black suit trio with red diamond, alternating high and low. \\
\rowcolor{negred} -- & 5ظآث 6ظآح 2ظآب 10ظآح Qظآث 2ظآح & Mixed suits; reds and blacks; sequential ranks; two kings. \\
\rowcolor{negred} -- & 8ظآخ 7ظآح 10ظآح Jظآخ Jظآث Qظآث & Black cards high, red cards low. \\
\rowcolor{negred} -- & 9ظآخ 8ظآح Kظآب Jظآح 6ظآح Qظآخ & Two reds, one black; high and low; alternating colors. \\
\rowcolor{negred} -- & Qظآح 6ظآخ 9ظآب 7ظآح Aظآب Aظآح & Two aces, red heart, black spades, queen and six. \\
\bottomrule
\end{longtable}


\subsection*{\colorbox{ruleblue}{\strut Exactly\_one\_club} (COUNT)}
\textbf{Rule:} Exactly one club

\begin{longtable}{C{0.5cm} L{4.5cm} L{9cm}}
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endfirsthead
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endhead
\rowcolor{posgreen} + & 5ظآث 7ظآب 7ظآب 6ظآح Aظآب Qظآخ & One red, one black, two sevens, an ace, and a queen. \\
\rowcolor{posgreen} + & 8ظآح Qظآب 3ظآخ 2ظآخ Qظآخ 5ظآث & One pair (Queens), two hearts, one spade, one club, red, black. \\
\rowcolor{posgreen} + & 7ظآب Aظآح 3ظآخ 8ظآح 4ظآث 3ظآخ & One red, two black, three diamonds. \\
\rowcolor{posgreen} + & 9ظآخ 4ظآح Jظآب 4ظآح Qظآث 4ظآخ & Four of a Kind - Hearts and Diamonds, Jack in Spades. \\
\rowcolor{posgreen} + & 9ظآب 3ظآح 9ظآخ Kظآخ Aظآح 10ظآث & 9ظآب 3ظآح 9ظآخ Kظآخ Aظآح 10ظآث - One pair, high card Ace. \\
\rowcolor{negred} -- & 8ظآب 4ظآخ 4ظآث 7ظآث 3ظآخ Jظآخ & Four diamonds, black and red, with a jack and two fours. \\
\rowcolor{negred} -- & 6ظآخ 4ظآب 10ظآح 10ظآخ 9ظآب 8ظآخ & Two red tens, a black nine, and a pair of sixes. \\
\rowcolor{negred} -- & 9ظآخ 6ظآح 6ظآخ 6ظآخ 2ظآث Kظآث & Three of a kind (6), high card king. \\
\rowcolor{negred} -- & 3ظآث 3ظآح 5ظآب 8ظآب 7ظآث 5ظآب & Black 3s and red 3s with a suited 5 and 8. \\
\rowcolor{negred} -- & 9ظآخ 9ظآث 5ظآث Aظآح Jظآخ 8ظآخ & A mixed-color straight with a pair. \\
\bottomrule
\end{longtable}


\subsection*{\colorbox{ruleblue}{\strut AP\_len3\_anywhere\_anyk} (AP)}
\textbf{Rule:} 3-term rank pattern with equal steps

\begin{longtable}{C{0.5cm} L{4.5cm} L{9cm}}
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endfirsthead
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endhead
\rowcolor{posgreen} + & 6ظآث Qظآب 9ظآث Aظآح 6ظآب Aظآح & A pair of sixes and aces, mixed red and black. \\
\rowcolor{posgreen} + & 4ظآخ 7ظآخ Kظآح Kظآب 10ظآح 4ظآح & Red cards, alternating faces, aces high. \\
\rowcolor{posgreen} + & 9ظآخ 10ظآخ Kظآح Jظآخ 3ظآح 8ظآح & Black suited high card flush. \\
\rowcolor{posgreen} + & 8ظآح 4ظآث Kظآث Qظآح 5ظآح 6ظآب & Black hearts, red clubs, high spade; two face cards, three number cards. \\
\rowcolor{posgreen} + & 10ظآخ 4ظآخ 6ظآب 7ظآث Jظآب 5ظآخ & Reds and blacks. Ten through Jack. Mixed suits. Clubs and spades dominate. \\
\rowcolor{negred} -- & 4ظآث Aظآث 2ظآح Aظآح Qظآث 2ظآب & Black and red spades, hearts, and clubs. Ace high, two pair. \\
\rowcolor{negred} -- & 7ظآخ Qظآث Kظآخ 6ظآب Kظآث 4ظآح & Black suits lead; high card contrasts with low. \\
\rowcolor{negred} -- & Qظآح 4ظآخ 3ظآخ 6ظآث 10ظآخ Qظآخ & Two queens, a red three, and a heart. \\
\rowcolor{negred} -- & Aظآخ Aظآخ 4ظآح 8ظآث Kظآث 5ظآح & Black Jacks and a colorful Ace. \\
\rowcolor{negred} -- & Kظآح Qظآث 6ظآخ 3ظآح Qظآب 10ظآخ & High card flush with alternating red and black. \\
\bottomrule
\end{longtable}


\subsection*{\colorbox{ruleblue}{\strut Half\_sum\_diff\_geN} (SCORE)}
\textbf{Rule:} Left half beats right by at least N points

\begin{longtable}{C{0.5cm} L{4.5cm} L{9cm}}
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endfirsthead
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endhead
\rowcolor{posgreen} + & 8ظآب 6ظآح Kظآب 6ظآخ 2ظآث 10ظآث & Black Jacks, Two Red Sixes, Clubs Ace, Deuce. \\
\rowcolor{posgreen} + & 10ظآح Kظآح 2ظآخ 9ظآث 4ظآخ 5ظآب & Two reds, one black; two hearts, three spades; a mix of high and low ranks. \\
\rowcolor{posgreen} + & Kظآث 9ظآخ 5ظآح Jظآح 3ظآخ 7ظآخ & Hearts: J, 5, K; Red. Diamonds: 9, 3, 7; Black. Alternating pattern. Mixed colors. High and low ranks. \\
\rowcolor{posgreen} + & 3ظآب Qظآب Kظآث 6ظآخ 2ظآخ 4ظآب & 3ظآب Qظآب Kظآث 6ظآخ 2ظآخ 4ظآب - Three spades, one club, alternating colors, ranks from 2 to Q. \\
\rowcolor{posgreen} + & Qظآخ Qظآخ 5ظآب 8ظآث 9ظآح 3ظآح & Two Queens, a 5, an 8, and two Hearts. \\
\rowcolor{negred} -- & 4ظآح 2ظآح Qظآخ 8ظآث Jظآث Qظآث & Two red hearts, two black clubs, one red diamond; queen high. \\
\rowcolor{negred} -- & 4ظآث Kظآب 8ظآب Kظآخ Kظآح 10ظآب & Four of a kind (Kings), one pair (Spades). \\
\rowcolor{negred} -- & 4ظآث 2ظآخ Jظآث 9ظآب 5ظآث 6ظآث & One club, two reds, Jack leads. \\
\rowcolor{negred} -- & 4ظآخ 8ظآخ 8ظآخ Aظآث 6ظآخ 3ظآح & Four reds, two eights, an ace. \\
\rowcolor{negred} -- & 2ظآح Jظآث 2ظآخ Jظآب 4ظآح 3ظآث & One pair, two different colors, alternating ranks. \\
\bottomrule
\end{longtable}


\subsection*{\colorbox{ruleblue}{\strut Halves\_uniform\_color\_equal} (HIER)}
\textbf{Rule:} Both halves uniform in color (or both not)

\begin{longtable}{C{0.5cm} L{4.5cm} L{9cm}}
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endfirsthead
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endhead
\rowcolor{posgreen} + & 10ظآث 5ظآح Jظآخ Aظآخ 5ظآث Aظآث & Ace high flush, alternating red and black. \\
\rowcolor{posgreen} + & Qظآخ Jظآث 4ظآح Aظآخ 4ظآخ Qظآث & Black queens, red jacks and fours, aces. \\
\rowcolor{posgreen} + & 4ظآح Qظآب 10ظآب Jظآح 9ظآب 10ظآخ & Spades high, reds low, alternating face cards. \\
\rowcolor{posgreen} + & Aظآب 9ظآح 5ظآب 4ظآح Qظآث 4ظآب & Black spades and red hearts, alternating. Queen in a card of each suit. \\
\rowcolor{posgreen} + & 2ظآخ 2ظآب 4ظآخ 3ظآح Kظآب 9ظآب & Two of hearts, two of spades, four of diamonds, king and nine of spades. \\
\rowcolor{negred} -- & 7ظآح 7ظآح 5ظآث 4ظآث 9ظآب 4ظآث & Two pairs, one club. \\
\rowcolor{negred} -- & Jظآث Qظآث Kظآث 10ظآث 2ظآح 2ظآب & Black flush with two red deuces. \\
\rowcolor{negred} -- & 4ظآب 9ظآح 8ظآب Qظآب 8ظآب 9ظآث & Four spades, two nines, a queen. \\
\rowcolor{negred} -- & 6ظآب Qظآث 10ظآث Qظآخ Qظآح Kظآث & One black suit, three red hearts, two queens and a king. \\
\rowcolor{negred} -- & 3ظآث Kظآب 4ظآخ 8ظآح 7ظآخ 9ظآخ & Heart diamonds, black spade, four unique cards. \\
\bottomrule
\end{longtable}


\subsection*{\colorbox{ruleblue}{\strut Halves\_hearts\_presence\_equal} (HIER)}
\textbf{Rule:} Both halves have heart or neither

\begin{longtable}{C{0.5cm} L{4.5cm} L{9cm}}
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endfirsthead
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endhead
\rowcolor{posgreen} + & 7ظآخ 8ظآب 5ظآح 9ظآح 6ظآخ 10ظآث & Mixed suits, alternating colors, sequential ranks. \\
\rowcolor{posgreen} + & Qظآخ 2ظآث 2ظآث Aظآخ 5ظآب 10ظآخ & Two pair, black, hearts and spades. \\
\rowcolor{posgreen} + & Jظآخ Kظآب 8ظآح 10ظآخ 8ظآخ 4ظآح & Two pairs, Jack and 8s. \\
\rowcolor{posgreen} + & Jظآث Aظآح 7ظآخ Kظآب 2ظآح 2ظآث & Two pair, hearts and clubs; one Ace. \\
\rowcolor{posgreen} + & 5ظآخ 5ظآب 7ظآب 4ظآث 5ظآب 4ظآث & Five of a kind: Two red 5s, two black 4s, and one 7. \\
\rowcolor{negred} -- & Kظآخ 4ظآب 7ظآث 7ظآخ 10ظآح 6ظآث & Two sevens, king and ten of different colors. \\
\rowcolor{negred} -- & 4ظآب 4ظآح 5ظآخ 8ظآب Aظآخ 9ظآخ & Four reds and two spades; high card diamond. \\
\rowcolor{negred} -- & Aظآخ 5ظآث Qظآح 9ظآث 3ظآخ 6ظآث & Reds \& blacks, alternating high and low. \\
\rowcolor{negred} -- & Aظآح Jظآح 7ظآخ 2ظآب Qظآث 8ظآخ & Heart Jack, Diamond Seven, Club Queen, mixed faces and colors. \\
\rowcolor{negred} -- & Kظآخ 10ظآب Jظآب 10ظآث Jظآح 9ظآخ & Two pair: Jacks and Tens. Clubs, Diamonds, and Spades. \\
\bottomrule
\end{longtable}


\subsection*{\colorbox{ruleblue}{\strut Well\_formed\_brackets\_by\_suit} (LANG)}
\textbf{Rule:} Suits form matched brackets

\begin{longtable}{C{0.5cm} L{4.5cm} L{9cm}}
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endfirsthead
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endhead
\rowcolor{posgreen} + & 7ظآب 3ظآخ Jظآح 6ظآث 2ظآث 3ظآث & Clubs lead, twos and threes mix. \\
\rowcolor{posgreen} + & 8ظآب 2ظآث Qظآخ Aظآح 6ظآث Jظآخ & Black, red, high card J. \\
\rowcolor{posgreen} + & 4ظآب Qظآح 7ظآث 6ظآث 2ظآب 4ظآح & Two spades, two hearts, two clubs. One pair, one three of a kind. Mixed colors, sequential ranks. \\
\rowcolor{posgreen} + & 8ظآب 9ظآح 4ظآب 6ظآح 2ظآخ Kظآخ & A heart spade mix with a king and two deuces. \\
\rowcolor{posgreen} + & 10ظآث 10ظآب 10ظآث 10ظآح 9ظآب 7ظآح & Four 10s, a 9, and a 7 in mixed suits. \\
\rowcolor{negred} -- & 9ظآح 8ظآب 10ظآخ 6ظآب Aظآخ 7ظآح & Black cards lead with a high ace. \\
\rowcolor{negred} -- & Qظآح 10ظآخ 10ظآث 10ظآح Aظآب 3ظآث & One red Queen, two black Tens, an Ace, and a Three. \\
\rowcolor{negred} -- & 3ظآث Qظآح Jظآب 4ظآح 2ظآث Jظآخ & Three of a kind (Jacks), mixed suits, red and black. \\
\rowcolor{negred} -- & 7ظآب Kظآث 7ظآح 4ظآث 10ظآث 6ظآب & 7ظآث Kظآخ 7ظآب 4ظآث 10ظآث 6ظآب \\
\rowcolor{negred} -- & 7ظآب 10ظآخ 3ظآخ 4ظآث 9ظآب 8ظآب & Black spades, red hearts; 3 unique ranks. \\
\bottomrule
\end{longtable}


\subsection*{\colorbox{ruleblue}{\strut Suits\_palindrome} (PAL)}
\textbf{Rule:} Suits read same forward/back

\begin{longtable}{C{0.5cm} L{4.5cm} L{9cm}}
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endfirsthead
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endhead
\rowcolor{posgreen} + & Jظآخ 10ظآح 9ظآخ 7ظآخ Kظآح Aظآخ & Ace-high straight flush with a mix of red and black cards. \\
\rowcolor{posgreen} + & Aظآب 10ظآب 10ظآح 10ظآح 2ظآب Qظآب & Two tens and a queen in red hearts. \\
\rowcolor{posgreen} + & Qظآث 4ظآب 5ظآخ 4ظآخ 3ظآب Qظآث & Two Queens and a pair of fours, one red, one black; a single three. \\
\rowcolor{posgreen} + & 5ظآخ Jظآح 5ظآب 7ظآب 4ظآح Jظآخ & Two Jacks and a Five of each suit. \\
\rowcolor{posgreen} + & 10ظآث 4ظآب 5ظآح 3ظآح 7ظآب 3ظآث & Black and red, two threes, a four, five, seven. \\
\rowcolor{negred} -- & 2ظآح 5ظآخ Qظآح 7ظآب Kظآب 5ظآث & Black jacks, red pairs. \\
\rowcolor{negred} -- & Jظآخ 6ظآح 9ظآخ 3ظآخ Aظآخ Jظآح & Two Jacks, one Ace, a Nine, and a Three, alternating red and black. \\
\rowcolor{negred} -- & 2ظآث 5ظآب 2ظآح Jظآخ 6ظآح 7ظآث & Two of a kind (Clubs and Hearts), Jack of Diamonds. \\
\rowcolor{negred} -- & Kظآث Jظآث 10ظآث 9ظآح Kظآث 2ظآح & Black, red, three kings, high flush. \\
\rowcolor{negred} -- & 9ظآح 2ظآح Qظآخ Jظآث 5ظآح 9ظآخ & Nine hearts, queen of diamonds, jacks clubs, five hearts, nine diamonds. \\
\bottomrule
\end{longtable}


\subsection*{\colorbox{ruleblue}{\strut Colors\_palindrome} (PAL)}
\textbf{Rule:} Colors read same forward/back

\begin{longtable}{C{0.5cm} L{4.5cm} L{9cm}}
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endfirsthead
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endhead
\rowcolor{posgreen} + & 3ظآح Qظآث 3ظآح 2ظآح 2ظآب 7ظآح & Three of hearts, Queen of clubs, two of hearts, two of spades, seven of hearts. \\
\rowcolor{posgreen} + & 10ظآب 6ظآح Qظآح 2ظآخ 9ظآح 7ظآث & 10ظآب, Qظآح, 9ظآح form a heart flush; pattern alternates red and black. \\
\rowcolor{posgreen} + & Jظآخ 7ظآخ 10ظآث 3ظآث Qظآخ 5ظآح & Two red jacks and queens with two black tens and threes. \\
\rowcolor{posgreen} + & 6ظآخ 8ظآب Aظآث 2ظآث 4ظآث Qظآخ & Reds, black club, high ace, sequential cards. \\
\rowcolor{posgreen} + & 7ظآث 9ظآب 5ظآب 8ظآث Qظآب Qظآث & Double flush: two black suits, triple queens. \\
\rowcolor{negred} -- & Aظآب 9ظآح 9ظآخ 5ظآث 10ظآب Jظآح & Black spades, red hearts and diamonds; two nines, five, ten, and jack. \\
\rowcolor{negred} -- & Jظآح Kظآخ 4ظآب 10ظآح 10ظآث 4ظآخ & J ظآحK ظآخ4 ظآب10 ظآح10 ظآخ4 \\
\rowcolor{negred} -- & Kظآح 2ظآب 3ظآخ Qظآث 6ظآب Jظآث & One black suit, two reds; alternating high and low ranks; diamonds and spades. \\
\rowcolor{negred} -- & 7ظآب Qظآخ 10ظآث Qظآخ 4ظآخ 7ظآح & Double Queens, alternating colors, two sevens. \\
\rowcolor{negred} -- & 5ظآح 7ظآخ 9ظآح 9ظآخ 2ظآخ 5ظآث & Two pair, hearts and diamonds; distinct colors. \\
\bottomrule
\end{longtable}


\subsection*{\colorbox{ruleblue}{\strut Halves\_copy\_suits} (COPY)}
\textbf{Rule:} Halves have same suit sequence

\begin{longtable}{C{0.5cm} L{4.5cm} L{9cm}}
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endfirsthead
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endhead
\rowcolor{posgreen} + & 5ظآب 4ظآح Jظآخ 2ظآب 5ظآح 4ظآخ & Two pairs of different ranks and colors. \\
\rowcolor{posgreen} + & Jظآث 5ظآخ 3ظآث 2ظآث 4ظآخ 8ظآث & Black, red, odd-numbered clubs, even-numbered diamonds. \\
\rowcolor{posgreen} + & 8ظآح 2ظآح 6ظآخ 4ظآح Kظآح Aظآخ & Hearts: Ace, King, Queen, Jack, Eight. Diamonds: Six, Four. Clubs: Two. Mixed colors, sequential ranks. \\
\rowcolor{posgreen} + & Aظآخ 8ظآح 7ظآخ Qظآخ 7ظآح 3ظآخ & Diamonds rule; two sevens; reds and blacks intermingle. \\
\rowcolor{posgreen} + & 3ظآح 3ظآب 8ظآح 9ظآح 5ظآب 8ظآح & Two sets of hearts and a singleton spade. \\
\rowcolor{negred} -- & Kظآب 3ظآب Jظآب 3ظآب 2ظآث Jظآخ & Black Jacks and threes, red heart. \\
\rowcolor{negred} -- & 10ظآث 3ظآح Qظآث 4ظآح 7ظآخ 6ظآب & Black: 10ظآث Qظآث 7ظآخ, Red: 3ظآح 4ظآح 6ظآب. Mixed suits, alternating colors. Queen high, varied ranks. \\
\rowcolor{negred} -- & 9ظآخ 2ظآب 9ظآح Kظآح Aظآب 8ظآخ & Two nines, a king, an ace, and a deuce; red, black, red. \\
\rowcolor{negred} -- & 10ظآث 10ظآح 6ظآب Kظآخ Jظآث 8ظآح & Two tens, a king, and an ace of hearts; a mix of black and red. \\
\rowcolor{negred} -- & Aظآح Kظآب 7ظآب 2ظآح 8ظآخ Qظآب & One red, two black, high to low hearts and spades. \\
\bottomrule
\end{longtable}


\subsection*{\colorbox{ruleblue}{\strut Adj\_same\_rank\_or\_suit} (ADJ)}
\textbf{Rule:} Neighbors share rank or suit

\begin{longtable}{C{0.5cm} L{4.5cm} L{9cm}}
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endfirsthead
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endhead
\rowcolor{posgreen} + & 10ظآح 10ظآح 10ظآب 7ظآب Aظآب 7ظآب & Two Tens and Two Sevens with an Ace in hearts. \\
\rowcolor{posgreen} + & 3ظآخ 3ظآح Aظآح 3ظآح 3ظآح Aظآح & Three of hearts, three diamonds, two aces. \\
\rowcolor{posgreen} + & 9ظآح 9ظآب Kظآب Kظآح Qظآح Jظآح & Black jacks, red queens. \\
\rowcolor{posgreen} + & 2ظآخ 2ظآث Jظآث Qظآث Qظآخ 5ظآخ & Two deuces and a queen flush. \\
\rowcolor{posgreen} + & Kظآب Kظآب 8ظآب 4ظآب Jظآب Jظآب & Black, spades, kings and jacks. \\
\rowcolor{negred} -- & Aظآخ 5ظآخ 5ظآث Qظآح 10ظآخ 8ظآب & Double pair of fives, high card queen. \\
\rowcolor{negred} -- & 3ظآح 8ظآخ Aظآح 10ظآح 8ظآث Qظآب & Black Jacks, two eights, Ace high, hearts lead. \\
\rowcolor{negred} -- & Kظآب 7ظآث 10ظآث Aظآث 5ظآح Qظآح & Black suits lead with a king, two sevens and tens follow, alternating reds include an ace and queen. \\
\rowcolor{negred} -- & 6ظآب 5ظآث 3ظآث 5ظآح 2ظآث 3ظآث & Black cards lead; two threes and a five heart. \\
\rowcolor{negred} -- & 2ظآب 10ظآخ 5ظآح 5ظآب 9ظآح 7ظآح & Black Jacks; Red Kings; Red Fives. \\
\bottomrule
\end{longtable}


\subsection*{\colorbox{ruleblue}{\strut Adj\_rank\_gap\_le3} (ADJ)}
\textbf{Rule:} Neighbors differ by ظëج3 ranks

\begin{longtable}{C{0.5cm} L{4.5cm} L{9cm}}
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endfirsthead
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endhead
\rowcolor{posgreen} + & 6ظآخ 6ظآح 3ظآث 6ظآب 5ظآح 7ظآب & Double sixes with hearts, three clubs, and a pair of spades. \\
\rowcolor{posgreen} + & 7ظآث 4ظآح 4ظآح 5ظآح 3ظآب 2ظآث & Black club, two red hearts, one black spade, sequential ranks. \\
\rowcolor{posgreen} + & 10ظآخ 7ظآب 4ظآح 2ظآب 4ظآث 4ظآث & Four cards of the same rank, two distinct. \\
\rowcolor{posgreen} + & 8ظآح 8ظآب 6ظآث 8ظآث 10ظآث Jظآب & Triple eights and a jack in hearts and spades. \\
\rowcolor{posgreen} + & 2ظآح 3ظآخ 4ظآث 6ظآح 4ظآخ 5ظآح & 2ظآح 3ظآخ 4ظآث 4ظآخ 5ظآح (Two hearts, one diamond, and two clubs) \\
\rowcolor{negred} -- & 3ظآخ Qظآح Jظآح 2ظآح 5ظآب 8ظآح & Hearts QJ258, mixed red and black. \\
\rowcolor{negred} -- & 10ظآح 10ظآب 10ظآخ 10ظآب 4ظآح 4ظآح & Two tens and two fours, alternating suits. \\
\rowcolor{negred} -- & Qظآب 2ظآح 6ظآخ 10ظآخ Aظآث 5ظآح & Ace high with alternating red and black cards. \\
\rowcolor{negred} -- & 3ظآث 8ظآخ 9ظآخ Aظآخ 5ظآح 9ظآخ & Double hearts, red ace, dark blue. \\
\rowcolor{negred} -- & 8ظآب 7ظآخ 10ظآح 2ظآث Aظآح Kظآح & Royal flush with a kicker. \\
\bottomrule
\end{longtable}


\subsection*{\colorbox{ruleblue}{\strut Only\_one\_odd\_rank} (PARITY)}
\textbf{Rule:} Exactly one odd rank

\begin{longtable}{C{0.5cm} L{4.5cm} L{9cm}}
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endfirsthead
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endhead
\rowcolor{posgreen} + & Aظآث 2ظآخ 3ظآح 6ظآخ Qظآث 8ظآب & Black cards lead with aces, hearts follow with 3s, and spades conclude. \\
\rowcolor{posgreen} + & 9ظآخ 8ظآخ 10ظآخ 6ظآخ 10ظآح Aظآخ & Black 4-card flush with a pair, diamond and heart. \\
\rowcolor{posgreen} + & 8ظآح Kظآح Qظآث 6ظآث 6ظآح 2ظآب & Black jacks, red sevens, alternating colors. \\
\rowcolor{posgreen} + & 6ظآح 10ظآب 2ظآث Qظآب 7ظآب 10ظآب & Black suit trio; one red heart; two tens, one queen. \\
\rowcolor{posgreen} + & Qظآخ 10ظآث 4ظآخ Kظآح 6ظآح 6ظآخ & One red suit, one black suit; high card queen, low card six. \\
\rowcolor{negred} -- & 5ظآب 8ظآح Jظآخ Aظآخ 7ظآخ 7ظآح & One spade, three red hearts and a diamond ace. \\
\rowcolor{negred} -- & Qظآح Qظآب 9ظآث Aظآب 6ظآث 7ظآخ & One spade, one heart, two clubs, alternating red and black, high and low ranks. \\
\rowcolor{negred} -- & Jظآح Kظآح Jظآخ Jظآب Qظآب Qظآح & Two Jacks and Two Queens, alternating colors. \\
\rowcolor{negred} -- & 7ظآخ 5ظآخ 10ظآح 3ظآخ Kظآث Aظآح & Seven reds, two blacks, one heart, one club. \\
\rowcolor{negred} -- & 3ظآخ 7ظآخ 6ظآخ 5ظآخ Jظآخ 6ظآث & Black and red, alternating diamonds and clubs. \\
\bottomrule
\end{longtable}


\subsection*{\colorbox{ruleblue}{\strut Uniform\_rank\_parity} (PARITY)}
\textbf{Rule:} All ranks same parity

\begin{longtable}{C{0.5cm} L{4.5cm} L{9cm}}
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endfirsthead
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endhead
\rowcolor{posgreen} + & 6ظآح Aظآخ 4ظآب 8ظآح 2ظآح 8ظآح & Four hearts, one red diamond, one black spade. \\
\rowcolor{posgreen} + & 2ظآخ Aظآب 4ظآث 2ظآخ 8ظآح Qظآب & Two twos, an ace, a four, an eight, and a queen. One suit repeated. Colors \\
\rowcolor{posgreen} + & Qظآب 8ظآث 8ظآح 10ظآث Qظآخ 4ظآث & Black jacks, double eights. \\
\rowcolor{posgreen} + & 8ظآح 8ظآخ 10ظآح 4ظآخ 10ظآث 10ظآب & Four tens with an eight kicker, alternating red and black. \\
\rowcolor{posgreen} + & 2ظآخ 10ظآب 8ظآث Aظآث 2ظآب 10ظآح & Two deuces, ten of spades, eight clubs, ace club, two spades, and ten hearts. \\
\rowcolor{negred} -- & 3ظآخ 2ظآح 5ظآح Qظآخ 6ظآح Aظآخ & High spades and hearts, queen leading the reds. \\
\rowcolor{negred} -- & 2ظآح Qظآث 7ظآث 2ظآخ 3ظآب 3ظآث & Two deuces, two threes, and a seven, alternating clubs and diamonds. \\
\rowcolor{negred} -- & 7ظآخ 10ظآخ 4ظآح Jظآخ 7ظآب Jظآب & Two pair: Jacks and Sevens, mixed colors. \\
\rowcolor{negred} -- & 5ظآح Qظآث 8ظآب 7ظآب Kظآخ 4ظآب & Black spades, red diamond; high face cards. \\
\rowcolor{negred} -- & 8ظآب Qظآب Kظآث Kظآث 4ظآب 3ظآخ & One pair Kings and a suited spade. \\
\bottomrule
\end{longtable}


\subsection*{\colorbox{ruleblue}{\strut Halves\_radial\_nonincreasing} (CENTER)}
\textbf{Rule:} Outward from center, ranks don't go up

\begin{longtable}{C{0.5cm} L{4.5cm} L{9cm}}
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endfirsthead
\toprule
\textbf{} & \textbf{Hand} & \textbf{LLM Description} \\
\midrule
\endhead
\rowcolor{posgreen} + & 4ظآب 4ظآب Jظآح 6ظآح 4ظآخ 2ظآب & Four-of-a-kind in black, Jack of hearts. \\
\rowcolor{posgreen} + & 7ظآح 8ظآث Kظآح 6ظآث 5ظآخ 3ظآب & Hearts \& Diamonds suit; alternating black and red cards; high King, mid-8, low 3. \\
\rowcolor{posgreen} + & 4ظآخ Jظآخ Jظآث 7ظآح 5ظآخ 4ظآح & Four of a kind, two pairs, mixed colors. \\
\rowcolor{posgreen} + & 3ظآح Qظآب Qظآخ 10ظآخ 8ظآث 8ظآث & One pair of Queens, two eights, hearts and spades. \\
\rowcolor{posgreen} + & 7ظآب 8ظآح 10ظآب 10ظآث 6ظآث 6ظآب & Two pairs, red and black. \\
\rowcolor{negred} -- & 9ظآث Kظآث 3ظآث 10ظآخ 2ظآح 5ظآخ & Black suited clubs and red hearts; one low ace. \\
\rowcolor{negred} -- & 7ظآخ 3ظآح Kظآث 6ظآخ 4ظآح Kظآخ & Two red kings, a black king, and two high-value cards. \\
\rowcolor{negred} -- & Aظآح 5ظآخ Qظآث Qظآخ 6ظآخ 7ظآخ & Red hearts, black clubs; diamond pair. \\
\rowcolor{negred} -- & 7ظآخ 8ظآخ 3ظآث 2ظآح Jظآب 6ظآث & Black suit majority; Jack leads the hearts; alternating red and black. \\
\rowcolor{negred} -- & Qظآح Jظآح Qظآب 2ظآخ 7ظآح 5ظآث & Two red queens, a diamond, and two black cards. \\
\bottomrule
\end{longtable}

\end{document}